---
title: "ps7"
author: "Jihye"
date: "3/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Prelim questions
#1. 
Who did you work with? binbin yiran
#2. 
20 hours
#3. 
???Yes, I have done the try.github.io tutorial.???

```{r}
library(tidyverse)
library(dbplyr)
library(lubridate)
```

# 1-1
```{r, eval=FALSE}
winsorize <- function(x, low = 0.01, high = 0.99) {
  if (is.numeric(x) == FALSE) {
    stop("X is not numeric", call. = FALSE)
  }
  qts <- quantile(x, prob = c(low, high))
  ifelse(x < qts[1], qts[1],
         ifelse(x > qts[2], qts[2]), x)
} 
```

# 1-2
```{r, eval=FALSE}
df <- tibble::tibble(
  a = rnorm(10),
  b = rnorm(10),
  c = rnorm(10),
  d = rnorm(10)
)

x <- df$a
(x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))

rescale01 <- function(x) {
  rng <- range(x, na.rm = FALSE) 
  (x - rng[1]) / (rng[2] - rng[1])
}

rescale01(c(3, 70, NA))
```      
If a vector x has at least one element what is NA, the whole vector will be affected so we cannot get rid of one specific NA. If na.rm = FALSE, the function would return NA for the whole vector anyway.

# 1-3
```{r, eval=FALSE}

rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE, finite = TRUE)
  y <- (x - rng[1]) / (rng[2] - rng[1])
  ifelse(y == Inf, 1,
         ifelse(y == -Inf, 0, y))
}

rescale01(c(Inf, -Inf, 0.5))

```

# 1-4
```{r, eval=FALSE}
mean(is.na(x))

x / sum(x, na.rm = TRUE)

sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)
```

```{r, eval=FALSE}
# mean
mean <- function(x) {
  mean(is.na(x))
}

mean(c(NA, 1, 2, 3))

# weight
weight <- function(x) {
  x / sum(x, na.rm = TRUE)
}
weight(c(1,2,3))

# sd/mean

#sdmean <- function(x) {
# sd <- sd(x, na.rm = TRUE)
#  mean <- mean(x, na.rm = TRUE)
#  y <- sd/mean
#  y
#}
#sdmean(runif(10))

# The syntax looks fine and it works on other computers but it doesn't work on my computer
```

# 1-5
```{r, eval=FALSE}
c1 <- c(1,2,3,NA)
c2 <- c(NA, 3, 2, 1)

both_na <- function(c1, c2) {
  sum(is.na(c1) & is.na(c2)) 
}

both_na(c1, c2)
```

# 1-6
```{r, eval=FALSE}
f1 <- function(string, prefix) {
substr(string, 1, nchar(prefix)) == prefix
}
f2 <- function(x) {
if (length(x) <= 1) return(NULL)
x[-length(x)]
}
f3 <- function(x, y) {
rep(y, length.out = length(x))
}

toy <- c("hello","hi","howareyou")
toy2 <- "hello"

# The function f1 returns a common prefix.
f1(toy, toy2)
# better name: prefix()

#The function f2 get rid of the the last element.
f2(toy)
# better name: rm_last().

#The function f3 repeats y.

f3(toy, toy2)
# better name: repeat()
```

# 1-7
```{r, eval=FALSE}
toy1 <- 2
toy2 <- 3
toy3 <- 4

if (toy1 > toy2) {
   print("t1 bigger than t2")
} else {
  print("t2 bigger than t1")
}

ifelse(toy2 > toy1, 
       ifelse(toy3 > toy2, "t3 bigger than t1 and t2", "t2 bigger than t3"), "t1 bigger than t2")
```    
If tests a single(first) condition but ifelse can test multiple elements.

# 1-8
```{r, eval=FALSE}
greeting <- function(time = lubridate::now()) {
  hr <- hour(time)
  ifelse(hr < 12, "Good morning!",
         ifelse(hr >= 12 & hr < 17, "Good afternoon!", "Good evening!"))
}

Sys.setenv("TZ"="America/Chicago")
greeting(now())
```

# 1-9
```{r, eval=FALSE}
fizzbuzz <- function(x) {
  stopifnot(length(x) == 1)
  stopifnot(is.numeric(x))
  if ((x %% 7) & (x %% 5)) {
    print("fizzbuzz")
  } else if (x %% 7) {
    print("fizz")
  } else if (x %% 5) {
    print("buzz")
  }
}

fizzbuzz(50)

```

# 1-10
```{r, eval=FALSE}

if (temp <= 0) { 
  "freezing"
} else if (temp <= 10) { 
  "cold"
} else if (temp <= 20) { 
  "cool"
} else if (temp <= 30) { 
  "warm"
} else { "hot"
}

cut(temp, c(-Inf, 0, 10, 20, 30, Inf), 
    labels = c("freezing", "cold", "cool", "warm", "hot"))

# if < instead of <= then use the argument FALSE
cut(temp, c(-Inf, 0, 10, 20, 30, Inf), right = FALSE,
    labels = c("freezing", "cold", "cool", "warm", "hot"))
```    
cut works for a more complicated vector rather than just a number    

# 1-11
```{r, error = TRUE}

x <- "a"

switch(x,
a = ,
b = "ab",
c = ,
d = "cd"
)
```

```{r, eval=FALSE}
x <- "e"
switch(x, 
       a=,
       b = "ab", 
       c=,
       d = "cd",
       stop("nothing matches")
)
```    
switch returns the "ab" for a or b
"cd" for c or d and an NULL for e. 
It returns the whole value if the first letter matches but returns NA when nothing matches.

# 1-12
```{r, eval=FALSE}
commas <- function(...) {
  stringr::str_c(..., collapse = ", ")
}

commas(letters, collapse = "-")

commas <- function(...) stringr::str_c(..., collapse = ", ")
commas(letters[1:10])
commas(letters, collapse = "-")
commas(letters, collapse = ",")

```

# 1-13
```{r, eval=FALSE}
rule <- function(..., pad = "-") {
  title <- paste0(...)
  width <- getOption("width") - nchar(title) - 5
  cat(title, " ", stringr::str_dup(pad, width), "\n", sep = "")
}
rule("Important output")
rule("Important output", pad = "-+")
rule("Important output", pad = "-+-")

#how can we fix it?
rule <- function(..., pad = "-") {
  title <- paste0(...)
  width <- getOption("width") - nchar(title) - 5
  padchar <- nchar(pad)
  cat(title, " ",
      stringr::str_dup(pad, width %/% padchar),
      stringr::str_sub(pad, 1, width %% padchar),
      "\n", sep = "")
}
rule("Important output")
rule("Important output", pad = "-+")
rule("Important output", pad = "-+-")

```

# 1-14    
Trim() cleans data by means of trimming, i.e., by omitting outlying observations.

# 2 R4DS Chapter 20 

# 2-1

```{r, eval=FALSE}
x <- c(3, NA, NaN)
is.finite(x)
!is.infinite(x)
```

# 2-2
```{r, eval=FALSE}
dplyr::near
```    
source:      
function (x, y, tol = .Machine$double.eps^0.5) 
{
    abs(x - y) < tol
}
<environment: namespace:dplyr>

# 2-3
currently R uses 32-bit integers, IEC 60559 floating-point.

# 2-4
```{r, eval=FALSE}
x <- c(0.01, 0.5, 0.99)
floor(x)
ceiling(x)
round(x, digits = 0) 
trunc(x)
signif(x, digits = 0)
```

floor() returns the biggest integer that is samller than x.
ceiling() returns the smallest interger that is larger than x.
round() is the same as floor() if x <= 0.5, the same as celing() if x>0.5
trunc is the same as floor
and signif gives the exact same numbers.

# 2-5
the three functiona are: parse_integer(), parse_logical(), and parse_double().

# 2-6
```{r, eval=FALSE}
x <- c(1,2,3, NA, NaN)
#mean(is.na(x))
#mean(!is.finite(x))
# error: evaluation nested too deeply: infinite recursion / options(expressions=)?
#Error during wrapup: evaluation nested too deeply: infinite recursion / #options(expressions=)?
```

mean(is.na(x)) returns the proportion of NAs in a vector 
mean(!is.finite(x)) returns the proportion of NA, NaN, or infinite.

# 2-7
```{r, eval=FALSE}
#1

x <- c(1,2,3,4,5)

last_value <- function(x) {
  if (length(x) <= 1) 
  x[length(x)]
}
last_value(x)

#2
position <- 40
even_position <- function(x) {
  if (position %% 2 == 0) {
    x[position %% 2 == 0]
  } else return(NULL)
}
even_position(x)

#3
non_last <- function(x) {
  if (length(x) <= 1) 
  x[-length(x)]
}
non_last(x)

#4
even_number <- function(x) {
  if (x %% 2 == 0) {
    x
  } else return(NULL)
}
even_number(x)
```

# 2-8
```{r, eval=FALSE}
(1:5)[13]
```   
subsetting with a positive integer that's bigger than the length of the vector returns NA.
subsetting with a name that doesn't exist returns an error.

# 2-9
```{r, eval=FALSE}
#knitr::include_graphics("drawing.pdf")
```



