---
title: "waze_ps7"
author: "Jihye"
date: "3/4/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(tidyverse)
library(RMySQL)
library(ggmap)
```

# 3 Waze JSON exploration

# 3-1
Three main datasets: alerts, jams and irregularities.   

In alerts, we have information on country, # of ThumbsUp, reportRating, confidence, reliability, type, uuid, roadType, magvar, subtype, street, location.    

In jams, we have information on country, city, level, line, speedKMH, length, turnType, type, uuid, speed, segments, roadType, delay, street   
    
In irregularities, we have information on country, # of Thumbsup, updatedate, trend, line, detectiondatemills, type, endnote, speed, seconds, jamlevel, highway, etc.

# 3-2
```{r}
waze_js <- fromJSON("https://na-georss.waze.com/rtserver/web/TGeoRSS?tk=ccp_partner&ccp_partner_name=University%20of%20Chicago&format=JSON&types=traffic,alerts,irregularities&polygon=-88.138000,42.112000;-87.569000,42.110000;-87.553000,41.511000;-88.132000,41.513000;-88.138000,42.112000;-88.138000,42.112000")
```

```{r, eval=FALSE}
alerts <- waze_js[[1]]
jams <- waze_js[[7]]
irregularities <- waze_js[[3]]

coord_pts <- alerts[[13]]
map <- get_map("chicago, illinois")

devtools::install_github("dkahle/ggmap")
devtools::install_github("hadley/ggplot2")
```

```{r}
#ggmap(map, extent = "normal") +
#  geom_point(data = coord_pts, aes(x = x, y = y), alpha = .5) +
#  ggtitle("Alerts in Chicago March 4 2018 4:08 pm")

#it doesn't work on my computer
```

#4 Waze SQL exploration

```{r, eval=FALSE}
require(tidyverse)
require(dbplyr)
require(RMySQL)
con <- DBI::dbConnect(RMySQL::MySQL(),
                      host = "uchicagowaze.cfykgneqoh8w.us-west-2.rds.amazonaws.com",
                      user = "ppha30531",
                      dbname='Waze2',
                      port = 3306,
                      password = .rs.askForPassword("Password")
)

DBI::dbListTables(con)
chi_sql <- tbl(con,"chiAlerts")
```

# 4-1
```{r, eval=FALSE}
chi_sql
chi_sql[1]
chi_sql[2]
```    

Variables included: country, # of thumbs up, city, report rating, confidence, reliability, type, uuid, road type, magvar and subtype.     
They don't provide information on the time, or sepcific location.   

# 4-2
```{r, eval=FALSE}
chi_sql %>% 
  select(country) %>%
  tally()

chi_sql %>% 
  select(uuid) %>%
  group_by(uuid) %>%
  tally()
```

There are 5380367 rows. 
There are 999 distinct uuid values, and 59 NAs.      
The server takes snapshot whenever I send a query.    

# 4-3
```{r, eval=FALSE}
chi_sql %>%
  select(type) %>%
  group_by(type) %>%
  tally()

chi_sql %>%
  select(type) %>%
  group_by(type) %>%
  tally() %>%
  show_query()

system.time(chi_sql %>% select(type) %>% group_by(type) %>% tally())
```

4 distinct alert types on the server, and some are NAs.     

The underlying SQL is:    
<SQL>
SELECT `type`, COUNT(*) AS `n`
FROM (SELECT `type`
FROM `chiAlerts`) `nqyfquaueg`
GROUP BY `type`     

It took 0.018 sec.      

# 4-4
```{r, cahe = TRUE, eval = FALSE}
system.time(type <- chi_sql %>%
              select(type) %>%
              collect())

type <- chi_sql %>%
  select(type) %>%
  collect()

system.time(n_distinct(type$type))   
```

It took 29.087 sec to download it to my computer.
and it took 0.2 sec to count the numbers. 

# 4-5
```{r, cache = TRUE, eval = FALSE}
system.time(chi_sql <- chi_sql %>%
  collect())

chi_sql <- chi_sql %>%
  collect()

ncol(chi_sql)
nrow(chi_sql)
```

Downloading the entire data took 377.7 seconds.
There are 5380367 rows and 17 columns in the only dataset - alerts.    

# 4-6
```{r}
# couldn't figure it out
```

# 4-7
```{r}
tb_long <- tribble(
  ~varaibel,            ~contents,                       ~logic,
  
  "country",           "Country",                        "TRUE",
  "nTHumbsUp",         "# of thumbs up",                 "FALSE",
  "city",              "City",                           "TRUE",
  "reportRating",      "Rating of the report",           "TRUE",
  "confidence",        "Confidence Level",               "TRUE",
  "reliability",       "Reliability Level",              "TRUE",
  "type",              "Alert type",                     "TRUE",
  "uuid",              "ID of the alert",                "FALSE",
  "roadType",          "Road Type",                      "TRUE",
  "magvar",            "Direction",                      "FALSE",
  "subtype",           "Subtype of the alert",           "TRUE",
  "street",            "Street",                         "FALSE",
  "location_x",        "Longitude",                      "FALSE",
  "location_y",        "Latitude",                       "FALSE",
  "pubMillis",         "?",                              "FALSE",
  "reportDescription", "Descrption of the report",       "FALSE",
  "scrape_dt",        "Date and time",                   "FALSE"
)
```

# 4-8
```{r, eval=FALSE}
chi_sql %>%
  select(scrape_dt, pubMillis) %>%
  mutate(date = as.POSIXct(pubMillis/1000, origin="1970-01-01", tz = "CST")) %>%
  head()
```

# 5 Explore specific events

# 5-1    
```{r, eval=FALSE}
df <- chi_sql %>%
  filter(uuid == "dcd95fd1-14d2-3f47-8981-ed39b220f99c") %>%
  collect()
```

```{r, eval=FALSE}
df[["scrape_dt"]] %>% first()
df[["scrape_dt"]] %>% last()
```
first: [1] "2017-11-27 01:10:00"
last: [1] "2017-11-27 05:05:00"    
Confidence and reliability changed.

# 5-2    
```{r, eval=FALSE}
df2 <- chi_sql %>%
  filter(uuid == "c5a73cc6-5242-3172-be5a-cf8990d70cb2") %>%
  collect()

df2 %>%
  filter(type == "JAM") %>%
  filter(as.Date(scrape_dt) == "2017-12-24") %>%
  filter(between(location_x, -87.5, -87.7) & between(location_y, 41.8 ,42.0)) 
```

# 5-3

```{r, eval=FALSE}
df3 <- chi_sql %>%
  filter(uuid == "79ff4897-0beb-3f6d-af79-934ad4925987") %>%
  collect()

df3
```    
the accident happened on W Lexington St around 2017-11-15 11-12 am at the location (-87.8	41.9)


